---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nycmaps

<!-- badges: start -->
<!-- badges: end -->

Provides sf objects of various New York City geographies (and associated tibbles of identifiers) for drawing thematic maps.

## Installation

You can install the development version of nycmaps like so:

``` r
remotes::install_github("kjhealy/nycmaps")
```

## Load

```{r}
library(tidyverse)
library(sf)
library(nycmaps)



# What's included

## Borough Boundaries

```{r}
nyc_boros

nyc_boros_sf
```


```{r}
ggplot(nyc_boros_sf) +
  geom_sf() +
  theme_void()
```


## Zip Codes (ZCTAs)

```{r}
nyc_zips

nyc_zip_sf
```

Notice that we have more zip codes in `nyc_zips` than zctas in `nyc_zip_sf`. Several of these zip codes are for PO Boxes or otherwise non-residential (like LGA and Fort Totten Park).

```{r}
nyc_zip_sf |>
  filter(pop == 0)
```


```{r}
ggplot(nyc_zip_sf) +
  geom_sf() +
  theme_void()
```

## Neighborhood Tabulation Areas

### NTA 2010

```{r}
nyc_nta10_sf
```

```{r}
ggplot(nyc_nta10_sf) +
  geom_sf() +
  theme_void()
```

### NTA 2020

```{r}
nyc_nta20_sf
```

```{r}
ggplot(nyc_nta20_sf) +
  geom_sf() +
  theme_void()
```

## Community District Tabulation Areas (CDTAs) 2020

```{r}
nyc_cdtas_2020_sf
```

```{r}
ggplot(nyc_cdtas_2020_sf) +
  geom_sf() +
  theme_void()
```

## Police Precincts

```{r}
nyc_police_precincts_sf
```

```{r}
ggplot(nyc_police_precincts_sf) +
  geom_sf() +
  theme_void()
```

## City Council Districts

```{r}
nyc_city_council_districts_sf
```

```{r}
ggplot(nyc_city_council_districts_sf) +
  geom_sf() +
  theme_void()
```

## Congressional Districts

```{r}
nyc_congressional_districts_sf
```

```{r}
ggplot(nyc_congressional_districts_sf) +
  geom_sf() +
  theme_void()
```

## Election Precincts

```{r}
nyc_election_precincts_sf
```

```{r}
ggplot(nyc_election_precincts_sf) +
  geom_sf() +
  theme_void()
```

## School Districts

```{r}
nyc_school_districts_sf
```

```{r}
ggplot(nyc_school_districts_sf) +
  geom_sf() +
  theme_void()
```

## State Assembly Districts

```{r}
nyc_state_assembly_districts_sf
```

```{r}
ggplot(nyc_state_assembly_districts_sf) +
  geom_sf() +
  theme_void()
```

## State Senate Districts

```{r}
nyc_state_senate_districts_sf
```

```{r}
ggplot(nyc_state_senate_districts_sf) +
  geom_sf() +
  theme_void()
```

## Municipal Court Districts

```{r}
nyc_municipal_court_districts_sf
```

```{r}
ggplot(nyc_municipal_court_districts_sf) +
  geom_sf() +
  theme_void()
```

## Public Use Microdata Areas (PUMAs)

### PUMAs 2010

```{r}
nyc_pumas_2010_sf
```

```{r}
ggplot(nyc_pumas_2010_sf) +
  geom_sf() +
  theme_void()
```

### PUMAs 2020

```{r}
nyc_pumas_2020_sf
```

```{r}
ggplot(nyc_pumas_2020_sf) +
  geom_sf() +
  theme_void()
```

## Fire Companies

```{r}
nyc_fire_companies_sf
```

```{r}
ggplot(nyc_fire_companies_sf) +
  geom_sf() +
  theme_void()
```

## Census Tracts

### Census Tracts 2000

```{r}
nyc_census_tracts_2000_sf
```

```{r}
ggplot(nyc_census_tracts_2000_sf) +
  geom_sf() +
  theme_void()
```

### Census Tracts 2010

```{r}
nyc_census_tracts_2010_sf
```

```{r}
ggplot(nyc_census_tracts_2010_sf) +
  geom_sf() +
  theme_void()
```

### Census Tracts 2020

```{r}
nyc_census_tracts_2020_sf
```

```{r}
ggplot(nyc_census_tracts_2020_sf) +
  geom_sf() +
  theme_void()
```

## Census Tract Population Proportions 2010-2020

```{r}
nyc_ct_pop_proportion_2010_2020_df
```

## Census Block Relationships 2020

```{r}
nyc_census_block_relationships_2020_df
```

## Census Tract to City Council District Relationships 2023

```{r}
nyc_ct_ccd_relationships_2023_df
```

## Census Tract Relationships 2020

```{r}
nyc_census_tract_relationships_2020_df
```

## Shoreline with Adjacent Areas

```{r}
nyc_shoclip_sf
```

```{r}
ggplot(nyc_shoclip_sf) +
  geom_sf() +
  theme_void()
```
